Analyzing X-ray images in Python with scikit-image

### 2016-08-22 skimage_tomo.tex
Edit for limitations section

\paragraph{Speed of execution.} Although \texttt{scikit-image} approaches
the speed of execution of compiled (C++, Java) code, it cannot reach the
performance of code optimized for the GPU. At the moment,
\texttt{scikit-image} is not the best tool for ultrafast computations
where the workflow is known beforehand, simple and stable. However, it is
an excellent tool for exploring image data interactively and testing
different algorithms -- an important component of data processing in
scientific work --, and its speed of execution is good enough to process
the gigabyte-sized tomographic images in seconds to minutes. Moreover,
multiprocessing capabilities of \texttt{scikit-image} should improve in
the future.

\paragraph{3-D compatibility.} At the moment, about two thirds of
\texttt{scikit-image} functions take indifferently 2D or 3D arrays. It is
planned to increase this compatibility in the future.

>>>>

\paragraph{Speed of execution.} Although \texttt{scikit-image} approaches
the speed of execution of compiled (C++, Java) code, it cannot reach the
performance of code optimized for the GPU. At the moment,
\texttt{scikit-image} is not the best tool for ultrafast computations
where the workflow is known beforehand, simple and stable. However, it is
an excellent tool for exploring image data interactively and testing
different algorithms -- an important component of data processing in
scientific work --, and its speed of execution is good enough to process
gigabyte-sized tomographic images in seconds to minutes. Moreover,
the multiprocessing capability of \texttt{scikit-image} should improve in
the near future.

\paragraph{3-D compatibility.} At the moment, about two thirds of
\texttt{scikit-image} functions transparently handle 2D or 3D arrays, with
the remainder limited to 2D analysis, often unnecessarily. Improved support
for 3D and higher-dimensional volumes is in the project roadmap, however.
